---
title: "example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(imprecise101)
```

## Examples 

We draw a sequence of marbles whose colours are (in order): blue, green, blue, blue, green, red. What conclusions can you reach about the probability of drawing a red marble on a future trial? 

If $\Omega = \{R, B, G, O\}$, then $n = (1, 3, 2, 0)$ and $L(\theta|n) \propto \theta_R \theta_B^3 \theta_G^2$. 

### 4.1. Probabilities of Future Outcomes 

The simplest way of stating our conclusion is to report the posterior upper and lower probabilities of obtaining red on the next trial. 

Using $s=2$, $\overline{P}(R|n)=0.375$ and $\underline{P}(R|n)=0.125$
For $s=1$, $\overline{P}(R|n)=0.286$ and $\underline{P}(R|n)=0.143$. 

```{r}
op <- idm(nj=1, s=2, N=6)
op$p.lower 
op$p.upper
```
